Community-Conditioned Language Models

### 2020-11-19 paper/paper.tex
comment out missing inputs
typography

\begin{table*}
  \centering
  \input{floats/info_gain.tex}
  \caption{Mean information gain of the CCLM over the baseline model, for messages in the test set.}
  \label{tab:model-info-gain}
\end{table*}

@@

\begin{table}
  \centering
  \input{floats/lmcc_gain.tex}
  \caption{
    Pearson's r correlation between community-wise information gain (of the CCLM over the un-conditioned model) and indescernibility.
  }
  \label{tab:lmcc_gain}
\end{table}

@@

We find that various communities exhibit widely varying levels of
linguistic complexity \cref{hyp:varying-complexity}, with perplexity
per-word ranging from less than 53 to 104 for the best model
architecture.

With indiscernibility values of 1.5 to 3.5 (out of a maximum of 46),
we find that CCLMs can be used to recognize communities based on
latent bayesian classification (\cref{hyp:LMCC-works}). Even the most
generic communities appear to exhibit fairly specific linguistic
patterns. Furthermore, these patterns are just as recognizable by LSTM
or Transformer models, when properly configured and trained.

We find a weak correlation \cref{tab:cclm_lmcc_ppl} between the perplexity of the \bn{I'm not sure if we can make this claim or not with the Ppl-Ppl correlations. However, given that *all* of them have positive correlation, even though the p-values are somewhat higher than .1 maybe we can?}
CCLM and the indiscernibility of the corresponding community
(\cref{hyp:rich-harder-to-identify}). Because we have relatively few,
and only large communities in our test set, it is difficult to
provide a conclusive answer, but this kind of correlation would suggest that
community-specific complexity can be partially attributed to using
more varied patterns. However, even the most complex communities
(perplexity per word above 100) have an indiscernibility of about 3
(out of a maximum of 46), so they retain fairly specific patterns:
they are not simply an even mixture of the kind of comments found in
other communities.

We find that the layer at which the community embedding is taken into
account in a CCLM influences its perplexity (\cref{hyp:layer-effect}),
albeit weakly. For LSTM models, the perplexity per word, averaged over
all communities, varies between 76.80 and 78.64. (with 80.70 for the unconditioned model)
The perplexity per word is slightly higher for $l_c=0$, and has very
little difference between the other models, with $l_c=1$ being the best.
For transformer models, it varies
between 89.38 and 122.56. Here perplexity per-word is clearly not a monotonous
function of $l_c$: the maximum is reached at $l_c=2$. We did not
expect non-mononicity, and leave studying this effect to future work.

The pattern of information gain by community is similar across architectures.
Communities that bennifit most from the conditioned model behave that way for 
both the LSTM and transformer.
However, there are some differences.
For example, the subreddit \emph{relationships} has an information gain of \num{1.018} for
the best CCLM LSTM but only \num{0.998} for the best transformer model. \bn{todo: community-wise CCLM info gain}
Why was the LSTM able to take advantage of the community information for
this community, where the transformer wasn't?
It would be interesting to investigate these differences in future work,
since it could reveal differences in the kind of linguistic variation the different
model architectures capture.

The representation of communities built by CCLM exhibits a clear
correlation with user-coocurrence patterns
(\cref{hyp:extra-linguistic-correlation}). A natural
question that may arise is how much this correlation can be explain by
user-specifc linguistic patterns. We plan to control for this variable
in future work, for example by building author-conditioned language
models and testing if community vector embeddings can be determined by
the set of the vector embeddings of its members.

>>>>

\begin{table*}
  \centering
  % \input{floats/info_gain.tex}
  \caption{Mean information gain of the CCLM over the baseline model, for messages in the test set.}
  \label{tab:model-info-gain}
\end{table*}

@@

\begin{table}
  \centering
  % \input{floats/lmcc_gain.tex}
  \caption{
    Pearson's r correlation between community-wise information gain (of the CCLM over the un-conditioned model) and indescernibility.
  }
  \label{tab:lmcc_gain}
\end{table}

@@

We find that various communities exhibit widely varying levels of
linguistic complexity \ref{hyp:varying-complexity}, with perplexity
per-word ranging from less than 53 to 104 for the best model
architecture.

With indiscernibility values of 1.5 to 3.5 (out of a maximum of 46),
we find that CCLMs can be used to recognize communities based on
latent bayesian classification \ref{hyp:LMCC-works}. Even the most
generic communities appear to exhibit fairly specific linguistic
patterns. Furthermore, these patterns are just as recognizable by LSTM
or Transformer models, when properly configured and trained.

We find a weak correlation (\cref{tab:cclm_lmcc_ppl}) between the perplexity of the \bn{I'm not sure if we can make this claim or not with the Ppl-Ppl correlations. However, given that *all* of them have positive correlation, even though the p-values are somewhat higher than .1 maybe we can?}
CCLM and the indiscernibility of the corresponding community
\ref{hyp:rich-harder-to-identify}. Because we have relatively few,
and only large communities in our test set, it is difficult to
provide a conclusive answer, but this kind of correlation would suggest that
community-specific complexity can be partially attributed to using
more varied patterns. However, even the most complex communities
(perplexity per word above 100) have an indiscernibility of about 3
(out of a maximum of 46), so they retain fairly specific patterns:
they are not simply an even mixture of the kind of comments found in
other communities.

We find that the layer at which the community embedding is taken into
account in a CCLM influences its perplexity \ref{hyp:layer-effect},
albeit weakly. For LSTM models, the perplexity per word, averaged over
all communities, varies between 76.80 and 78.64. (with 80.70 for the unconditioned model)
The perplexity per word is slightly higher for $l_c=0$, and has very
little difference between the other models, with $l_c=1$ being the best.
For transformer models, it varies
between 89.38 and 122.56. Here perplexity per-word is clearly not a monotonous
function of $l_c$: the maximum is reached at $l_c=2$. We did not
expect non-mononicity, and leave studying this effect to future work.

The pattern of information gain by community is similar across architectures.
Communities that bennifit most from the conditioned model behave that way for 
both the LSTM and transformer.
However, there are some differences.
For example, the subreddit \emph{relationships} has an information gain of \num{1.018} for
the best CCLM LSTM but only \num{0.998} for the best transformer model.
Why was the LSTM able to take advantage of the community information for
this community, where the transformer wasn't?
It would be interesting to investigate these differences in future work,
since it could reveal differences in the kind of linguistic variation the different
model architectures capture.

The representation of communities built by CCLM exhibits a clear
correlation with user-coocurrence patterns
(\ref{hyp:extra-linguistic-correlation}). A natural
question that may arise is how much this correlation can be explain by
user-specifc linguistic patterns. We plan to control for this variable
in future work, for example by building author-conditioned language
models and testing if community vector embeddings can be determined by
the set of the vector embeddings of its members.
